---
source: Rmd
title: "Introduction to RStudio"
teaching: 10
exercises: 2
questions:
- "How to use RStudio?"
objectives:
- "Understand the functions of each of the 4 main panels in RStudio."
- "Practice opening, writing, and running code in an Rscript."
- "Explain the philosophy and design of tidyverse."
- "Demonstrate loading data into R and making a plot."
keypoints:
- "Edit the .Rmd files not the .md files"
- "Run `make serve` to knit documents and preview lesson website locally"
---

## What is R?



If the lesson uses additional packages, the script that converts the Rmd files
into markdown, will detect them and install them for you, when you run `make
serve` or `make site`.

This first chunk is really important, and need to be included at the beginning of
each episode written in RMarkdown.

```{r, echo=TRUE}
source("../bin/chunk-options.R")
```

The rest of the lesson should be written as a normal RMarkdown file. You can
include chunk for codes, just like you'd normally do.

Normal output:

```{r}
1 + 1
```

Output with error message:

```{r}
x[10]
```

Output generating figures:

```{r plot-example}
library(ggplot2)
ggplot(diamonds, aes(x = carat,  y = price, color = cut)) +
    geom_point()
```

For the challenges and their solutions, you need to pay attention to where the
`>` go and where to leave blank lines. You can include code chunks in both the
instructions and solutions. For instance this:

```
> ## Challenge: Can you do it?
>
> What is the output of this command?
>
> ```{r, eval=FALSE}
> paste("This", "new", "template", "looks", "good")
> ```
>
> > ## Solution
> >
> > ```{r, echo=FALSE}
> > paste("This", "new", "template", "looks", "good")
> > ```
> {: .solution}
{: .challenge}
```

will generate this:

> ## Challenge: Can you do it?
>
> What is the output of this command?
>
> ```{r, eval=FALSE}
> paste("This", "new", "template", "looks", "good")
> ```
>
> > ## Solution
> >
> > ```{r, echo=FALSE}
> > paste("This", "new", "template", "looks", "good")
> > ```
> {: .solution}
{: .challenge}

{% include links.md %}
