---
source: Rmd
title: "Introduction to RStudio"
teaching: 30
exercises: 2
questions:
- "How do we use RStudio?"
objectives:
- "Understand the functions of each of the 4 main panels in RStudio."
- "Practice opening, writing, and running code in an Rscript."
- "Explain the philosophy and design of tidyverse."
- "Demonstrate loading data into R and making a plot."
keypoints:
- "RStudio tracks data, plots, variables, we create or load into R"
- "Rscripts are short segements of code saved to text documents that can be run over and over"
- "Enter and run R code from scripts to build a foundation of code for future analysis"
---

## What is R?

R is an open-source software environment developed originally for statistical computing and graphics
originally released in 1995. Since then, it has expanded significantly, becoming a prominent 
comuputer language, a major platform for open-source software development and distribution, and 
garnering a strong global community. 

R's strong background in statistical computation, readibility, and open-source development has set 
it apart from many other computing languages as one of the most important environments for data 
analysis, and it is used widely for this purpose in academia, finance, and the healthcare industry.

R can be used by opening a terminal and entering

```
> ## Bash
> R
```
```
> ## Output
> R version 3.6.1 (2019-07-05) -- "Action of the Toes"
> Copyright (C) 2019 The R Foundation for Statistical Computing
> Platform: x86_64-pc-linux-gnu (64-bit)
>
> R is free software and comes with ABSOLUTELY NO WARRANTY.
> You are welcome to redistribute it under certain conditions.
> Type 'license()' or 'licence()' for distribution details.
>
>  Natural language support but running in an English locale
>
> R is a collaborative project with many contributors.
> Type 'contributors()' for more information and
> 'citation()' on how to cite R or R packages in publications.
>
> Type 'demo()' for some demos, 'help()' for on-line help, or
> 'help.start()' for an HTML browser interface to help.
> Type 'q()' to quit R.
>
> >
```

## What is RStudio?

W



## What

Learning how to use R involves learning to use its programming language. R does simplify writing 
scripts in a number of ways compared to other programming languages, but it is still challenging to 
learn for those without a background in computer programming.While this language can be entered and 
run line-by-line in a terminal, like using BASH, more complicated tasks often require code to be 
run in chunks, called *scripts*. 



One way

If the lesson uses additional packages, the script that converts the Rmd files
into markdown, will detect them and install them for you, when you run `make
serve` or `make site`.

This first chunk is really important, and need to be included at the beginning of
each episode written in RMarkdown.

```{r, echo=TRUE}
source("../bin/chunk-options.R")
```

The rest of the lesson should be written as a normal RMarkdown file. You can
include chunk for codes, just like you'd normally do.

Normal output:

```{r}
1 + 1
```

Output with error message:

```{r}
x[10]
```

Output generating figures:

```{r plot-example}
library(ggplot2)
ggplot(diamonds, aes(x = carat,  y = price, color = cut)) +
    geom_point()
```

For the challenges and their solutions, you need to pay attention to where the
`>` go and where to leave blank lines. You can include code chunks in both the
instructions and solutions. For instance this:

```
> ## Challenge: Can you do it?
>
> What is the output of this command?
>
> ```{r, eval=FALSE}
> paste("This", "new", "template", "looks", "good")
> ```
>
> > ## Solution
> >
> > ```{r, echo=FALSE}
> > paste("This", "new", "template", "looks", "good")
> > ```
> {: .solution}
{: .challenge}
```

will generate this:

> ## Challenge: Can you do it?
>
> What is the output of this command?
>
> ```{r, eval=FALSE}
> paste("This", "new", "template", "looks", "good")
> ```
>
> > ## Solution
> >
> > ```{r, echo=FALSE}
> > paste("This", "new", "template", "looks", "good")
> > ```
> {: .solution}
{: .challenge}

{% include links.md %}
